### 2011-09-15 Text/paper.tex
Minor revisions.

\section{Other boundary conditions}
We used the outflow boundary conditions for both boundaries and determined the coefficient
according Eq. \ref{theor:continuous:mass:transfer}. One can see the calculated mass transfer
coefficient in time in Fig. \ref{fig:steady:state:jos}.
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/steady_state_jos.eps}
\caption{The calculated mass transfer coefficient in time with open boundaries $\partial_x
C_{inlet}=\partial_x C_{outlet}=0$. One can see some negative values for volumetric coefficients.
This situation corresponds to the case, then the inlet concentration is greater than the outlet
$C_{inlet}>C_{outlet}$. This corresponds to smaller capillary numbers due to vortex in front of the
bubble. It is the indication that one needs to take more time steps to wait until the outlet
concentration becomes larger than the inlet, which can take a relatively large time period to
wait. Large numbers of the volumetric mass transfer coefficients means the insuffient number of
the unit volumes simulated, as the large difference in the outlet and inlet numbers means the
deviation from the continuous picture. \label{fig:steady:state:jos} }
\end{figure}

>>>>

\section{Other boundary conditions}
We used the outflow boundary conditions for both boundaries and determined the coefficient
according Eq. \ref{theor:continuous:mass:transfer}. One can see the calculated mass transfer
coefficient in time in Fig. \ref{fig:steady:state:jos}.
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/steady_state_jos.eps}
\caption{The calculated mass transfer coefficient in time with open boundaries $\partial_x
C_{inlet}=\partial_x C_{outlet}=0$. One can see some negative values for volumetric coefficients.
This situation corresponds to the case, then the inlet concentration is greater than the outlet
$C_{inlet}>C_{outlet}$. This corresponds to smaller capillary numbers due to vortex in front of the
bubble. It is the indication that one needs to take more time steps to wait until the outlet
concentration becomes larger than the inlet, which can take a relatively large time period to
wait. Large numbers of the volumetric mass transfer coefficients means the insuffient number of
the unit volumes simulated, as the large difference in the outlet and inlet numbers means the
deviation from the continuous picture. \label{fig:steady:state:jos} }
\end{figure}
If two domains are joined together then results are quite different. One can see them in Fig.
\ref{fig:steady:state:jos:double}.
\begin{figure}
\includegraphics[width=\textwidth]{Figures/steady_state_double_jos.eps}
\caption{The mass transfer coefficient versus time for doubled domain. One can see that the
volumetric mass transfer coefficients are smaller in comparison with one unit volume simulation. As
well one needs to wait longer time as the mass comes from one bubble to another bubble. 
\label{fig:steady:state:jos:double}}
\end{figure}
